### 2019-10-15 ch6_bred/content.tex
update bred

\subsection{The Cancer Genome Atlas}
We downloaded all available RNA-seq profiles from The Cancer Genome Atlas. In total, we computed case-wise GRNs for 14'963 tumour samples from 50 sub-projects, including 44 different cancer entities.

@@

% going forward: functional validation; benchmark against in silico datasets; 
% can also use TI instead of clustering

@@

\subsection{Data from the Tabula Muris project}

\subsection{Data from The Canger Genome Atlas project}

>>>>

\subsection{The Cancer Genome Atlas}
We included all available RNA-seq profiles from The Cancer Genome Atlas. In total, we computed case-wise GRNs for 14'963 tumour samples from 50 sub-projects, including 44 different cancer entities. Clusters of case-wise GRNs were relabelled by the project they originate from, or by the cell types or organs the samples originate from.

Most groups of interactions are highly specific to just one cancer type. Samples from the CPTAC project were split into two groups, clustering together with LUAD (lung adenocarcinoma) and kidney carcinoma samples. According to the meta-information of CPTAC profiles, these samples consist of lung, kidney, and uterus adenocarcinomas, explaining the split in CPTAC samples.

%TODO: Extend !!

@@

The \texttt{bred} algorithm is a novel approach for directly computing case-wise GRNs for single-cell omics and bulk omics profiles alike. We applied the method to 22'122 hematopoietic cells and 14'963 cancer profiles, showing that interactions are often grouped together in modules specific for certain cell types, tissue types, or cancer types.

In this work, we only applied clustering methods to the case-specific 'regulome profiles', but other types of computational methods can be used to annotate and explore case-specific GRNs, such as trajectory inference and differential expression.

Going forward, we will provide further functional validation of the results generated by \texttt{bred}, as well as benchmark the algorithm against various real and \textit{in silico} datasets.

@@

%\subsection{Data from the Tabula Muris project}
%
%\subsection{Data from The Cancer Genome Atlas project}
